The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-01-09 analysis/paper/paper.qmd

```{r}
#| label: setup
#| echo: false
library(tidyverse)
library(tmap)
```

>>>>

```{r}
#| label: setup
library(dplyr)
library(readr)
library(stringr)
devtools::load_all(".")

# read csv file with pages that are useful for the analysis
emu_theses <- read_csv(here::here("analysis","data", "raw_data", "emu-theses.csv")) %>%
  mutate(pdf_filename = paste0(year, "-", author_surname, ".pdf")) %>%
  mutate(text = "")

pdf_paths<- here::here("analysis","data", "raw_data", emu_theses$pdf_filename)

emu_theses$text <- convert_pdf_text(pdf_paths)

# clean text 
  emu_theses$text_clean <- emu_theses$text %>%
    str_replace_all("\\s", " ") %>%  ### remove all carriage return and newline characters
    str_squish() %>%
    str_replace_all("- ", "") %>%       ### remove all hyphens
    str_replace_all("[0-9]", "") %>%    ### remove all numbers
    str_replace_all(emu_theses$author_firstname, "") %>%   ### remove author first name
    str_replace_all(emu_theses$author_surname, "") %>%     ### remove author surname
    str_replace_all(emu_theses$title, "") %>%              ### remove title
    # str_replace_all("Claudiu Forgaci", "") %>%
    # str_replace_all("Bucharest: Between North and South", "") %>%
    str_replace_all("EMU", "")          ### remove common words
```
